Social Conditions of Fear

### 2023-11-28 scripts/manuscript.qmd
table

```{r}
#| label: mice imputation
# DO NOT RUN 
complete5 <- mice(na_data, 
                 m = 50, 
                 seed = 25)

@@

```{r}
```

>>>>

```{r}
#| label: mice imputation
#| eval: false
complete5 <- mice(na_data, 
                 m = 5, 
                 seed = 25)

@@

```{r}
#| label: creating a smaller subset from data

gss_subset <- tidydata %>% 
  select(age, sexnow1, racecombo, uscitzn, degree, attend, raclive, happy, health, 
         partnrs5, fear) 
```

```{r}
#| label: tbl-fear_race
#| tbl-cap: Table showing mean fear by race.

gss_subset %>% 
  pivot_longer(
    cols = fear,
    names_to = "fear",
    values_to = "answer") %>% 
  select(racecombo, answer) %>% 
  mutate(fear = as.numeric(case_when(answer == "no" ~ "0",
                                 answer == "yes" ~ "1"))) %>% 
  select(racecombo, fear) %>% 
  group_by(racecombo) %>% 
  summarize(mean_fear = mean(fear)) %>% 
  kable(caption = "Mean Social Fear by Race",
        col.names = c("Race", "Mean"),
        digits = 3)
```

```{r}
#| label: fig-fear_race
#| fig-cap: Bar graph showing the proportion or respondants, by race, that feared walking alone at night.

gss_subset %>% 
  filter(!is.na(racecombo)) %>% 
  filter(racecombo != "Other") %>% 
  ggplot(aes(x = racecombo, y = after_stat(prop), group = fear, 
             fill = fear)) +
  geom_bar(position = "dodge") + 
  scale_y_continuous(labels = scales::percent) +
  labs(title = "Social Fear by Race",
       caption = "Question: Is there any area right around here--that is, within a mile--where you would be afraid to walk alone at night?",
       x = "Race",
       y = NULL,
       fill = "Fear"
       ) +
  theme_bw()
